Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-05-11 paper.qmd
Update
Update with new package

sc_ltr_pos <- c(0.08, 0.96)
sc_xlims <- c(-0.25, 1.25)
sc_ylims <- c(-0.25, 1.9)
# sc_xlims <- c(-0.25, 1.25)
# sc_ylims <- c(-0.25, 2)

@@

## Hexagonal binning to have regular hexagons
hb_obj_scurve <- hex_binning(
  data = umap_scurve_scaled, 
  bin1 = num_bins_x_scurve, 
  s1 = -0.06, 
  s2 = -0.06, 
  r2 = r2)

>>>>

sc_ltr_pos <- c(0.08, 0.96)
sc_xlims <- c(-0.25, 1.25)
sc_ylims <- c(-0.4, 1.9)
# sc_xlims <- c(-0.25, 1.25)
# sc_ylims <- c(-0.25, 2)

@@

## Hexagonal binning to have regular hexagons
hb_obj_scurve <- hex_binning(
  data = umap_scurve_scaled, 
  bin1 = num_bins_x_scurve, 
  q = 0.1,
  r2 = r2)
